%\begingroup
%\let\cleardoublepage\clearpage


\chapter*{Abstract}
\markboth{Abstract}{Abstract}
\addcontentsline{toc}{chapter}{Abstract} % adds an entry to the table of contents

\vspace{0.5cm}

In recent years, CRM's editors have gain interest in investigating artificial intelligence solutions. Companies need to personalize their offers and processes to create a strong relationship with their clients. This personalization of offers is supported by customer relationship management (CRM) systems containing the entire company's knowledge about its customers. With the advent of artificial intelligence, the large amounts of data stored in a CRM can be used by a company to adopt a real customer-centric strategy.

This study starts with an overview of the artificial intelligence solutions offered by CRM's editors. The goal is to understand the uses of these solutions, their incorporation into business processes, the types of artificial intelligence techniques used as well as the efforts and implications required to integrate them. The results indicate that all major CRM players have and are investing heavily in this market, but some of them took the lead with more features offered. Connections and integrations with other solutions will be important to have intelligent CRM systems.

A proof-of-concept is developed to demonstrate how a machine learning project can be created from CRM data and integrated directly into business processes. Based on a fully connected neural network, the model predicts the date of customers next order in a very competitive market. The predictions enable a company to plan the future and understand client's needs before they occur.

\vspace{0.7cm}

\texttt{ \justifyi \textbf{KEYWORDS}: Customer relationship management, CRM AI, customer data, event prediction}

%\endgroup			
%\vfill
